Keyword and Collocation analysis on India-related text of *Natural History*

### 2023-08-24 paper_quarto.qmd
0824 collocation part update

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of *Natural History*"
author: "Dawn, Lizao Zhuang (r0914937)"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
echo: false
warning: false
tbl-cap-location: top
bibliography:
  - references.bib
  - packages.bib  
csl: unified-style-sheet-for-linguistics.csl
abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder. The study focuses on uncovering prominent themes and topics associated with India in the context of the book. The research employs collocate examination techniques and keyword analysis to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
---

@@

The initial obeservation shown in @fig-top20geoname and @fig-geonamemap leads to a focus to the India-related text for this study. With a reference to *Barrington Atlas of the Greek and Roman World* (@talbert2000; @talbert2000-1), the approximate geographical coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:

@@

Textual collocation refers to the frequently occurring word with the target word in the context. Different from the surface collocation, which only taking the word left and right to the target word, the word span in this case refers to the "textual units" around the target word. Setting "India" as the target word in the corpus of all paragraphs in *Natural History*, the `mclm::text_cooc()` function returns the frequency of words observed in the context of "India". As mentioned in the Methodology Section (@sec-method), the returned scores were filtered for those having PMI scores higher than 2 and signed $G^2$ scores higher than 3.84, in order to gain a strong and significant word list co-occurring with word "India" in the context.

@@

@tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 collocates associated with the word "india" in the entire text, respectively sorted by G_signed and PMI scores. As the returned $G^2$ score helps gauge the strength of evidence regarding the independence between the two words [@montes2022], thereby facilitating the initial sorting.

@@

### Sorted by G_singed

@@

```
:::

Similar to the results of keyword analysis, the top 20 sorted list of absolute frequency and G singed have a 11/20 overlapped outputs. As shown in @fig-col_colloc, the signed G score and absolute frequency in textual collocation has a positibe correlation.

```{r}
#| label: fig-col_colloc
#| fig-cap: Correlation of signed G and absolute frequency in textual collocation

@@

The high-ranking words of textual collocation with "India" in the work are cateforized as follows, those without specifying the association measurement are the overlapped ones:

**Geographical**: arabia, indian, ethiopia, ganges, indus(G)

**Numeric**: hundred, thousand(A), whole(A)

**Time**: year (A)

**Merchandise exchange**: mart(G)

**Precious Stone/Gem**: stones, rock-crystal, gems, pearls, gem(G), gemstone(G)

**Animal/Plant**: elephants, gum(A), lustre(G)

**Historical Figure**: alexander(A), megasthenes(G), onesicritus(G)

**Descriptive expression**: numerous(A), luxury(A), closely(A), valuable(A), bright(A), identical(G), smaragdus(G)

**Others**: shadow(A)

The top 20 collocates associated with the word "India," sorted by their $G^2$ scores, reveal three key dimensions:

1.  **Geographical Connections**: The collocates such as *arabia*, *ethiopia*, *east*, *south*, *opposite*, and *beyond* indicate the geographical relationships and proximity between India and these regions.

2.  **Trading and Imports**: The presence of collocates like *imported*, *produces*, *produce* and *nations* suggests that India had a significant role in trade and the importation of goods. It also implies that India was known for producing various commodities that were sought after by other nations.

3.  **Boundaries and Borders**: The collocates *boundary*, *set* and *part* indicate the existence of defined boundaries or borders related to India. This suggests that there were recognized territorial demarcations associated with India during the referenced period.

```{r}
coocs_ref_df <- as_tibble(coocs$ref_freqlist)
words_to_check_colloc <- c("arabia", "indian", "ethiopia", "ganges", "rock-crystal", "hundred", "elephants", "megasthenes", "indians", "gem", "lustre", "stones", "identical", "'smaragdus", "indus", "gems", "gemstone", "pearls", "onesicritus", "mart")
filtered_top_scores_colloc <- top_scores_colloc_df %>%
  filter(type %in% words_to_check_colloc)

@@

results_colloc <- tibble(
  Word = filtered_top_scores_colloc$type,
  Target_Frequency = filtered_top_scores_colloc$a,
  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
) %>% 
  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

```{r}

@@

results_colloc_pmi <- tibble(
  Word = filtered_top_scores_colloc$type,
  Target_Frequency = filtered_top_scores_colloc$a,
  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
) %>% 
  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

>>>>

---
engine: knitr
title: "Keyword and Collocation analysis on India-related text of *Natural History*"
author: "Dawn, Lizao Zhuang (r0914937)"
format: 
  html:
    theme: journal
    toc: true
    code-link: true
    abstract-title: "Abstract"
number-sections: true
echo: false
warning: false
tbl-cap-location: top
fig-cap-location: top
bibliography:
  - references.bib
  - packages.bib  
csl: unified-style-sheet-for-linguistics.csl
abstract: 'This paper presents a comprehensive analysis of keywords and collocates related to India in a corpus of Natural History by Pliny the Elder. The study focuses on uncovering prominent themes and topics associated with India in the context of the book. The research employs collocate examination techniques and keyword analysis to reveal significant insights into the perception and imagination of India, as a competent counterpart to the Roman Empire, by Pliny the Elder and the scholars of his time.'
---

@@

The initial obeservation shown in @fig-top20geoname and @fig-geonamemap leads to a focus to the India-related text for this study. With a reference to *Barrington Atlas of the Greek and Roman World* [@talbert2000; @talbert2000-1], the approximate geographical coordinates defining the Indian region during the time of *Natural Hisoty* are as follows[^3]:

@@

Textual collocation refers to the observation of some words frequently occurring with the target word in the context. Different from the surface collocation, which taking the collocating span, i.e. the certain words left and right to the target word into consideration [@evert2009], the word span in this case refers to the textual unit around the target word. Setting "India" as the target word in the corpus of all paragraphs in *Natural History*, the `mclm::text_cooc()` function returns the frequency of words appeared in the context of "India". As mentioned in the Methodology Section (@sec-method), the returned scores are filtered with a statistical criteria for gaining a list of the most frequently observed words in the context of word "India" with strong significance.

@@

@tbl-coltable_absolute_freqencies, @tbl-coltable_Gsigned and @tbl-coltable_PMI display the top 20 contextual collocates associated with the word "india", respectively sorted by PMI, absolute frequency signed $G^2$ scores.

::: panel-tabset

### Sorted by absolute frequencies

@@

### Sorted by Signed $G^2$

@@

:::

The top 20 ranking lists of absolute frequency and signed $G^2$ scores have a 11/20 overlapped outputs. As shown in @fig-col_colloc, the signed $G^2$ score and absolute frequency in textual collocation analysis shows a positive correlation.

```{r}
#| label: fig-col_colloc
#| fig-cap: Scatter plot of signed $G^2$ scores and absolute frequency in textual collocation analysis

@@

The high-ranking words in textual collocation with "India" sorted by absolute frequency and signed $G^2$ scores are categorized as follows, those without specifying the association measures ("A" stands for "absolute frequency" and "G" stands for "signed $G^2$ scores") are the overlapped ones. These words listed out comprises the strongest evidence of collocating with "India" in the context.

**Geographical connections**: *arabia*, *indian*, *ethiopia*, *ganges*, *indus*(G)

**Animal/Plant**: *elephants*, *gum*(A), *lustre*(G)

**Precious Stone**: *stones*, *rock-crystal*, *gems*, *gem*(G), *gemstone*(G), *pearls*

**Historical Figure**: *alexander*(A), *megasthenes*(G), *onesicritus*(G)

**Merchandise exchange**: *mart*(G)

**Descriptive expression**: *hundred*, *thousand*(A), *whole*(A), *numerous*(A), *luxury*(A), *closely*(A), *valuable*(A), *bright*(A), *identical*(G), *smaragdus*(G)

**Others**: *shadow*(A), *year*(A)

These categories indicates that the narrative about "India" in *Natural History* covers three major dimensions. The first dimension is its geographical situation, including its connection to other places (mainly Arabia and Ethiopia), the two major rivers, Ganges and Indus within the region, and the animals, plants and precious stones originated in it. And it is often mentioned with historical figures, some related to the conquest history of the Roman Empire (in the case of *alexander*, referring to Alexander the Great, who had conducted several expeditions to Indian subcontinent), and some related to the referencing scholarship Pliny made his dialogue with. Moreover, the collocating word *mart* and the descriptive expressions highlights the merchandise exchanges introduced and discussed in the India-related content in the work.

In the `mclm::text_cooc()` function, the given text will be separated as target context (text surrounding the target node) and reference context (text not surrounding the target node). As checked in the @tbl-colloc_freq_compare_AFG, not all words with both high absolute frequency and signed $G^2$ scores showing more frequency than that in the reference context.

```{r}
#| label: tbl-colloc_freq_compare_AFG
#| tbl-cap:  Frequency comparison of overlapping textual collocating words sorted by absolute frequency and signed $G^2$ score in the top 20 ranking in target and reference context

coocs_ref_df <- as_tibble(coocs$ref_freqlist)
words_to_check_colloc <- c("arabia", "indian", "ethiopia", "ganges", "rock-crystal", "hundred", "elephants", "megasthenes", "indians", "gem", "lustre", "stones", "identical", "'smaragdus", "indus", "gems", "gemstone", "pearls", "onesicritus", "mart")
filtered_top_scores_colloc <- top_scores_colloc_df %>%
  filter(type %in% words_to_check_colloc)

@@

results_colloc <- tibble(
  Word = filtered_top_scores_colloc$type,
  Target_Frequency = filtered_top_scores_colloc$a,
  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
) %>% 
  arrange(desc(Target_Frequency)) %>% 
  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

While in the top 20 list sorted with PMI scores, as shown in @tbl-colloc_frequency_compare_PMI, all of the results shows higher frequency than that in the reference context.
```{r}
#| label: tbl-colloc_frequency_compare_PMI
#| tbl-cap:  Frequency comparison of top 20 textual collocating words sorted by PMI score in target and reference context

@@

results_colloc_pmi <- tibble(
  Word = filtered_top_scores_colloc$type,
  Target_Frequency = filtered_top_scores_colloc$a,
  Reference_Abs_Frequency = abs_freq_lookup1[filtered_top_scores_colloc$type],
  Reference_Nrm_Frequency = nrm_freq_lookup1[filtered_top_scores_colloc$type]
) %>% 
  arrange(desc(Target_Frequency)) %>%
  kbl(col.names = c("Type", "Target_Frequency", "Reference_Abs_Frequency", "Reference_Nrm_Frequency")) %>% 
  kable_minimal() %>% 
  scroll_box(height = "400px")

@@

The PMI word list shows more descriptive information about the theme related to India in *Natural History*.
